Learning how to act: making good decisions with machine learning

### 2017-07-08 thesis/offcuts.tex
finishes off contextual bandits and off-policy evaluation section drafts

>>>>

\subsection{Markov decision processes}

\subsubsection{Limitations of bandit problems}
\begin{itemize}
\item Reward needs to be observed immediately after action is taken (or at least before the next action must be selected).
\item State assumed not to change

\end{itemize}

Reward known immediately. Action chosen for one individual does not effect reward for the next (SUTVA).

A key limitation of the bandit setting is that

This is reasonable in settings where we have many similar but independent units or individuals and the goal is to identify which action is optimal (in a given context), as occurs in standard experimental settings as well.

Relation to SUTVA assumption, selecing a action for one 'unit' does not effect the reward distributions for other units.

The reward of an action is not immediately known. - a long sequence of steps. Delayed reward.

In the bandit setting the reward distributions for each arm are assumed to be fixed. A much studied generalisation is the Markov decision process or MDP. In an MDP we assume there the environment has some state. The reward an agent receives depends on the state of the environment and the action the agent selects. The environment then evolves stochastically depending on the agents action. Multi-armed bandits can be considered a single state MDP, where no matter what action the agent selects, the environment returns to that state.

Insert a graphical representation of an MDP

What assumptions are required to make MDPs tractable.

What is the basic algorithm (Q-learning)

What are the key results.

\subsubsection{Dynamic Systems}
\begin{itemize}
\item An explicit model of actions in a partially known system (eg HMM)
\item Feynman-Kac Lemma; Solving a PDE can be converted to a stochastic process
\end{itemize}

\subsection{The need to add structure}
The regret for a bandit problem grows linearly with the number of (sub-optimal) actions. This makes problems with large or infinite actions spaces intractable. REFERENCE equation showing linearity with arms. CHECK ITS TRUE.

causal bandits capture a very natural form of structure that can arise between different arms.

The classic multi-armed bandit is a powerful tool for sequential decision making. However, the regret grows linearly with the number of (sub-optimal) actions and many real world problems have large or even infinite action spaces. This has led to the development of a wide range of models that assume some structure across the reward distributions for different arms, for example generalised linear bandits \cite{filippi2010parametric}, dependent bandits \cite{Pandey2007}, X-armed bandits \cite{Bubeck2010} and Gaussian process bandits \cite{srinivas2009gaussian}, or that consider more complex feedback, for example the recent work on graph feedback \cite{Mannor2011,Lelarge2012,Alon2013,Buccapatnam2014,Kocak2014,Alon2015} and partial monitoring \cite{Piccolboni2001,Bartok2014}.

\section{Questions}
\begin{enumerate}
\item In the $\epsilon$-greedy approach, does one compute best action based only on exploration steps?
\item Why does the naive reduction appear to get sub-optimal regret?
\item When does the expected regret make sense as the thing we actually would wish to optimise? Is optimising the expected regret any different to optimising the psuedo-regret? Who is the definition of regret down to? Does this definition of regret come from learning with expert advise?
\item Is there a reference for the doubling trick? Is it an automatic way of converting a fixed horizon algorithm to an anytime one?
\item Is Learning from logged feedback data just covariate shift too?
\item In contextual bandits, does it ever make sense that $Y$ causes $X$? If the reward is some function of the action taken and the context, then the full vector of counterfactual outcomes $Y$ is never instantiated. Are there any implications of this for inference?
\item Why does anything solving a regression problem work in the anti-causal direction - it would seem to break the fundamental underlying assumption of additive noise?
\item is there a benchmark library of implementations of key bandit algorithms?
\item Bubeck 2012 states that if the adversary is oblivious, the psuedo-regret coincides with the standard regret, 'which is always the ultimate quantity of interest'. Why, they are not the same for stochastic bandits are they?
\item what is the worst-case regret of UCB in an adversarial setting?
\item is there a concept of problem dependent regret for adversarial bandits? Has there been analysis of the problem dependent regret for key adversarial algorithms such as EXP-3?
\item adversarial regret bounds for Thompson sampling, UCB with random arm selection from upper-bound set?
\item do continuous armed bandits implie that there are arms with any arbitrary gap in reward (including worst case gap for that T) and thus you always end up with something like worst case regret?)
\item in what real world setting do adversarial bandits potentially make sense?
\item Does supervised learning really 'reveal the value of every action'.
\end{enumerate}

### 2017-07-08 thesis/thesis_map.tex
finishes off contextual bandits and off-policy evaluation section drafts

\renewcommand{\P}[1]{\operatorname{P}\left(#1\right)}
\newcommand{\cf}[2]{{#1}^{#2}}
\newcommand{\bernoulli}{\operatorname{Bernoulli}}
\newcommand{\dirac}{\operatorname{Dirac}}
\newcommand{\parents}[1]{\operatorname{\mathcal{P}a}_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\regret}{\bar{R}_{T}} %psuedo-regret
\newcommand{\expectedregret}{\mathbb{E}R_{T}} % expected regret
\newcommand{\rawregret}{R_{T}} % plain regret
\newcommand{\simpleregret}{R_T}
\newcommand{\quotes}[1]{``#1''}

@@

\vspace{0.5cm}
\begin{definition}[Stochasitic k-armed bandit problem]
Let $\actionspace = \set{1,...k}$ be the set of available actions (or bandit arms) and $\P{\vec{Y}} = \P{Y_1,...,Y_k}$ be the joint distribution over the rewards for each action. The multi-armed bandit problem proceeds over $T$ rounds. In each round $t$, 
\begin{enumerate}
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the actions and rewards from previous time-steps and a (potentially stochastic) \emph{policy} $\pi$
\item the world stochastically generates the rewards for each action, $[Y_{t,1},...,Y_{t,k}] \sim \P{\vec{Y}}$
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate}
At the end of the game the total reward obtained by the learner is $\sum_{t=1}^T Y_{t,a_t}$. We denote the expected reward for the action $i$, $\E{ \P{Y_i}}$, by $\mu_i$ and the action with the highest expected reward by $i^*$. 
\end{definition}

@@

The form of the dependence on the number of arms $k$ and horizon $T$ differs between the problem dependent and worst case regret. The problem dependent regret grows linearly with the number of arms, $k$, and logarithmically with $T$. The difference stems from the fact the problem dependent regret defines how the regret grows for a given set of reward distributions as $T$ increases, whereas in the worst case regret, the gap between expected rewards is varied as a function of $T$. \citet{Auer1995} show that the worst case regret for the k-armed bandit problem is lower bounded by,

\eqn{
\label{eqn:k-arm-bandit-lower-bound}
\regret \in \bigomega{\sqrt{kT}}
}

@@

\vspace{0.5cm}
\begin{definition}[Stochastic Contextual Bandit \footnote{Contextual bandits can also be defined in the adversarial setting analagously to definition \ref{def:adversarial-k-armed-bandit}}]
\label{def:contextual-bandit-problem}
Let $\P{\vec{Y},\vec{X}}$ be the joint distribution over the rewards for each action and some context $\vec{x} \sim \mathcal{X}$. In each round $t \in \set{1,...T}$, 
\begin{enumerate}
\item the world stochastically generates the vector of rewards for each action and the context, $([Y_{t,1},...,Y_{t,k}],\vec{x}_t) \sim \P{\vec{Y},\vec{X}}$ and reveals $\vec{x}_t$ to the learner
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the context as well as actions and rewards from previous time-steps.
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate}
\end{definition}

@@

\eqn{
\label{eqn:regret_contextual}
\regret = \max_{h \in \mathcal{H}}\E{\sum_{t=1}^T{Y_{t,h(\vec{x}_t)}}} - \E{\sum_{t=1}^T{Y_{t,a_t}}}
}

@@

Suppose that, at each timestep $t$, after selecting an action, the learner recieved the reward for chosen action but observed the full vector of rewards $[Y_{t,1},...,Y_{t,k}]$. This is known as the full information setting. In this case, the learner can simulate running each hypothosis over the history to compute the reward it would have obtained and use the hypothosis with the best empirical reward to select the next action. This is the \emph{follow the leader} algorithm, which obtains optimal regret $\bigo{\sqrt{T log(\card{\mathcal{H}})}}$ for the full-information problem \citep{cesa2006prediction}. Unfortunately, in the contexual bandit problem, the (counterfactual) rewards associated with alternate action choices are not observed. As in causal effect estimation, we can view this as a missing data problem. However, the data is missing not at random because which component of the reward is observed depends on the action selected which in turn is a function of the previous history of actions and rewards.

@@

\eqn{
\argmax_{h \in \mathcal{H}} \sum_{t=1}^\tau Y_t \ind{h(\vec{x}_t) = a_t}
}

@@

Finally, if we have a parametric model for the relationship between context, action and reward that allows (efficient) computation of the posterior or confidence bounds on the reward for each arm given context, we can develop generalized versions of the UCB or Thompson sampling algorithms. For linear pay off models, both approaches yield algorithms with strong regret guarantees, Lin-UCB \citep{li2010contextual} and generalised thompson sampling for linear pay-offs \citep{Agrawal2013}.

It is worth noting that definition \ref{def:contextual-bandit-problem} does not make any assumptions about the \emph{causal} relationship between the context $\vec{X}$ and the reward $\vec{Y}$, see figure \ref{fig:contextual-bandit-causal-graph}. \citet{Bareinboim2015} demonstrate that policies that incorporate observations of the action an agent would have taken were their action not set by the bandit policy can acheive lower regret than those that ignore this information. This is an example of the case represented in figure \ref{fig:context-graph-confounded}. However, the context should be relevent, such that $\P{\vec{Y}|\vec{X}} \neq \P{\vec{Y}}$, otherwise including it is the equivelent to adding irrelevent featurs to a supervised learning problem.

\begin{figure}[h]
\centering
\caption{Several potential causal graphical models for the contextual bandit problem (if actions are selected at random). $\vec{X}$ and $\vec{Y}$ represent the context and reward vectors respectively, and $Y = \vec{Y}_a$ is the reward recieved by the learner, which is a deterministic function of $\vec{Y}$ and $a$. Regardless of the causal structure, observing the context $\vec{X}$ provides information about the vector of rewards $\vec{Y}$. To represent a realistic (contextual) bandit problem, where actions are not selected at random, we would need to \quotes{unroll} the graphs, such that there was a copy for each time-step $t$ and allow the action $a_t$ to depend on the context $\vec{X}_t$ and the previous observations $(\vec{X},a,Y)_1^{t-1}$. }
\label{fig:contextual-bandit-causal-graph}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{X}$ causes $\vec{Y}$}
\label{fig:context-graph-causal}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$a$};
\node[main node, left=of 1](4){$\vec{X}$};
 \path[every node/.style={font=\sffamily\small}]
   (4) edge (1)
   (3) edge (2)
   (1) edge (2);
\end{tikzpicture} 
\end{subfigure}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{Y}$ causes $\vec{X}$}
\label{fig:context-graph-anti-causal}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$a$};
\node[main node, left=of 1](4){$\vec{X}$};
 \path[every node/.style={font=\sffamily\small}]
   (1) edge (4)
   (3) edge (2)
   (1) edge (2);
\end{tikzpicture} 
\end{subfigure}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{X}$ and $\vec{Y}$ are counfounded}
\label{fig:context-graph-confounded}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$a$};
\node[main node, left=of 1](4){$\vec{X}$};
\node[lt, below=of 4](5){$U$};
 \path[every node/.style={font=\sffamily\small}]
   (3) edge (2)
   (1) edge (2)
   (5) edge (4) edge (1);
\end{tikzpicture}
\end{subfigure}
\end{figure}

\subsubsection{Learning from logged bandit data}
Another topic of interest within the contextual bandit community that is deeply related to causal effect estimation from observational data is learning from logged bandit feedback data \citep{}.

If no assumptions are made about the behaviour of the hypothosis that generated the data.... does it reduce to causal effect estimation?

However, in the applications considered in these setting such as ad serving, the details of the hypothosis generating the data are often known.

\subsection{Markov decision processes}

\subsubsection{Limitations of bandit problems}
\begin{itemize}
\item Reward needs to be observed immediately after action is taken (or at least before the next action must be selected).
\item State assumed not to change

Reward known immediately. Action chosen for one individual does not effect reward for the next (SUTVA).

A key limitation of the bandit setting is that

This is reasonable in settings where we have many similar but independent units or individuals and the goal is to identify which action is optimal (in a given context), as occurs in standard experimental settings as well.

Relation to SUTVA assumption, selecing a action for one 'unit' does not effect the reward distributions for other units.

The reward of an action is not immediately known. - a long sequence of steps. Delayed reward.

In the bandit setting the reward distributions for each arm are assumed to be fixed. A much studied generalisation is the Markov decision process or MDP. In an MDP we assume there the environment has some state. The reward an agent receives depends on the state of the environment and the action the agent selects. The environment then evolves stochastically depending on the agents action. Multi-armed bandits can be considered a single state MDP, where no matter what action the agent selects, the environment returns to that state.

Insert a graphical representation of an MDP

What assumptions are required to make MDPs tractable.

What is the basic algorithm (Q-learning)

What are the key results.

\subsubsection{Dynamic Systems}
\begin{itemize}
\item An explicit model of actions in a partially known system (eg HMM)
\item Feynman-Kac Lemma; Solving a PDE can be converted to a stochastic process
\end{itemize}

\subsection{The need to add structure}
The regret for a bandit problem grows linearly with the number of (sub-optimal) actions. This makes problems with large or infinite actions spaces intractable. REFERENCE equation showing linearity with arms. CHECK ITS TRUE.

causal bandits capture a very natural form of structure that can arise between different arms.

The classic multi-armed bandit is a powerful tool for sequential decision making. However, the regret grows linearly with the number of (sub-optimal) actions and many real world problems have large or even infinite action spaces. This has led to the development of a wide range of models that assume some structure across the reward distributions for different arms, for example generalised linear bandits \cite{filippi2010parametric}, dependent bandits \cite{Pandey2007}, X-armed bandits \cite{Bubeck2010} and Gaussian process bandits \cite{srinivas2009gaussian}, or that consider more complex feedback, for example the recent work on graph feedback \cite{Mannor2011,Lelarge2012,Alon2013,Buccapatnam2014,Kocak2014,Alon2015} and partial monitoring \cite{Piccolboni2001,Bartok2014}.

\section{Questions}
\begin{enumerate}
\item In the $\epsilon$-greedy approach, does one compute best action based only on exploration steps?
\item Why does the naive reduction appear to get sub-optimal regret?
\item When does the expected regret make sense as the thing we actually would wish to optimise? Is optimising the expected regret any different to optimising the psuedo-regret? Who is the definition of regret down to? Does this definition of regret come from learning with expert advise?
\item Is there a reference for the doubling trick? Is it an automatic way of converting a fixed horizon algorithm to an anytime one?
\item Is Learning from logged feedback data just covariate shift too?
\item In contextual bandits, does it ever make sense that $Y$ causes $X$? If the reward is some function of the action taken and the context, then the full vector of counterfactual outcomes $Y$ is never instantiated. Are there any implications of this for inference?
\item Why does anything solving a regression problem work in the anti-causal direction - it would seem to break the fundamental underlying assumption of additive noise?
\item is there a benchmark library of implementations of key bandit algorithms?
\item Bubeck 2012 states that if the adversary is oblivious, the psuedo-regret coincides with the standard regret, 'which is always the ultimate quantity of interest'. Why, they are not the same for stochastic bandits are they?
\item what is the worst-case regret of UCB in an adversarial setting?
\item is there a concept of problem dependent regret for adversarial bandits? Has there been analysis of the problem dependent regret for key adversarial algorithms such as EXP-3?
\item adversarial regret bounds for Thompson sampling, UCB with random arm selection from upper-bound set?
\item do continuous armed bandits implie that there are arms with any arbitrary gap in reward (including worst case gap for that T) and thus you always end up with something like worst case regret?)
\item in what real world setting do adversarial bandits potentially make sense?
\item Does supervised learning really 'reveal the value of every action'.
\end{enumerate}

>>>>

\renewcommand{\P}[1]{\operatorname{P}\left(#1\right)}
\newcommand{\cf}[2]{{#1}^{#2}}
\newcommand{\cfb}[2]{{#1}_t^{#2}} % used to represent reward
\newcommand{\bernoulli}{\operatorname{Bernoulli}}
\newcommand{\dirac}{\operatorname{Dirac}}
\newcommand{\parents}[1]{\operatorname{\mathcal{P}a}_{#1}}
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\newcommand{\regret}{\bar{R}_{T}} %psuedo-regret
\newcommand{\expectedregret}{\mathbb{E}R_{T}} % expected regret
\newcommand{\rawregret}{R_{T}} % plain regret
\newcommand{\simpleregret}{R_T}
\newcommand{\quotes}[1]{``#1''}

@@

\vspace{0.5cm}
\begin{definition}[Stochasitic k-armed bandit problem]
Let $\actionspace = \set{1,...,k}$ be the set of available actions (or bandit arms) and $\P{\vec{y}} = \P{y_1,...,y_k}$ be a joint distribution over the rewards for each action. The multi-armed bandit problem proceeds over $T$ rounds. In each round $t$, 
\begin{enumerate}
\item the learner selects an action $a_{t} \in \set{1,...,k}$, based on the actions and rewards from previous time-steps and a (potentially stochastic) \emph{policy} $\pi$
\item the world stochastically generates the rewards for each action, $[Y_{t,1},...,Y_{t,k}] \sim \P{\vec{y}}$
\item the learner observes and recieves (only) the reward for the selected action $Y_{t,a_t}$ 
\end{enumerate}
At the end of the game the total reward obtained by the learner is $\sum_{t=1}^T Y_{t,a_t}$. We denote the expected reward for the action $i$ by $\mu_i$ and the action with the highest expected reward by $i^*$. 
\end{definition}

@@

The form of the dependence on the number of arms $k$ and horizon $T$ differs between the problem dependent and worst case regret. The problem dependent regret grows linearly with the number of arms, $k$, and logarithmically with $T$. The difference stems from the fact the problem dependent regret defines how the regret grows for a given set of reward distributions as $T$ increases, whereas in the worst case regret, the gap between expected rewards is varied as a function of $T$. \citet{Auer1995} show that the worst case regret for the k-armed bandit problem is lower bounded by $\regret \in \bigomega{\sqrt{kT}}$

@@

\vspace{0.5cm}
\begin{definition}[Stochastic Contextual Bandit \footnote{Contextual bandits can also be defined in the adversarial setting analagously to definition \ref{def:adversarial-k-armed-bandit}}]
\label{def:contextual-bandit-problem}
Let $\P{\vec{x},\vec{y}}$ be the joint distribution over the rewards for each action and some context $\vec{X} \in \mathcal{X}$. In each round $t \in \set{1,...T}$, 
\begin{enumerate}
\item the world stochastically generates the vector of rewards for each action and the context, $(\vec{X}_t,[\cfb{Y}{1},...,\cfb{Y}{k}]) \sim \P{\vec{x},\vec{y}}$ and reveals $\vec{X}_t$ to the learner
\item the learner selects an action $A_{t} \in \set{1,...,k}$, based on the context as well as actions and rewards from previous time-steps,
\item the learner observes and recieves (only) the reward for the selected action $Y_t = \cfb{Y}{A_t}$ 
\end{enumerate}
\end{definition}

@@

\eqn{
\label{eqn:regret_contextual}
\regret = \max_{h \in \mathcal{H}}\E{\sum_{t=1}^T{\cfb{Y}{h(\vec{X}_t)}}} - \E{\sum_{t=1}^T{\cfb{Y}{A_t}}}
}

@@

Suppose that, at each timestep $t$, after selecting an action, the learner recieved the reward for chosen action but observed the full vector of rewards $[\cfb{Y}{1},...,\cfb{Y}{k}]$. This is known as the full information setting. In this case, the learner can simulate running each hypothosis over the history to compute the reward it would have obtained and use the hypothosis with the best empirical reward to select the next action. This is the \emph{follow the leader} algorithm, which obtains optimal regret $\bigo{\sqrt{T log(\card{\mathcal{H}})}}$ for the full-information problem \citep{cesa2006prediction}. Unfortunately, in the contexual bandit problem, the (counterfactual) rewards associated with alternate action choices are not observed. As in causal effect estimation, we can view this as a missing data problem. However, the data is missing not at random because which component of the reward is observed depends on the action selected which in turn is a function of the previous history of actions and rewards.

@@

\eqn{
\argmax_{h \in \mathcal{H}} \sum_{t=1}^\tau Y_t \ind{h(\vec{X}_t) = A_t}
}

@@

Finally, if we have a parametric model for the relationship between context, action and reward that allows (efficient) computation of the posterior or confidence bounds on the reward for each arm given context, we can develop generalized versions of the UCB or Thompson sampling algorithms. For linear pay-off models, both approaches yield algorithms with strong regret guarantees, \emph{Lin-UCB} \citep{li2010contextual} and \emph{Generalised Thompson Sampling} \citep{Agrawal2013}.

It is worth noting that definition \ref{def:contextual-bandit-problem} does not make any assumptions about the \emph{causal} relationship between the context $\vec{X}$ and the reward $\vec{Y}$, see figure \ref{fig:contextual-bandit-causal-graph}. \citet{Bareinboim2015} demonstrate that policies that incorporate observations of the action an agent would have taken were their action not set by the bandit policy can acheive lower regret than those that ignore this information. This is an example of the case represented in figure \ref{fig:context-graph-confounded}. However, the context should be relevent, such that $\P{\vec{y}|\vec{x}} \neq \P{\vec{y}}$, otherwise including it is the equivelent to adding irrelevent featurs to a supervised learning problem.

\begin{figure}[h]
\centering
\caption{Several potential causal graphical models for the contextual bandit problem (if actions are selected at random). $\vec{X}$ and $\vec{Y}$ represent the context and reward vectors respectively, and $Y = \vec{Y}^a$ is the reward recieved by the learner, which is a deterministic function of $\vec{Y}$ and $a$. Regardless of the causal structure, observing the context $\vec{X}$ provides information about the vector of rewards $\vec{Y}$. To represent a realistic (contextual) bandit problem, where actions are not selected at random, we would need to \quotes{unroll} the graphs, such that there was a copy for each time-step $t$ and allow the action $A_t$ to depend on the context $\vec{X}_t$ and the previous observations $(\vec{X},A,Y)_1^{t-1}$. }
\label{fig:contextual-bandit-causal-graph}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{X}$ causes $\vec{Y}$}
\label{fig:context-graph-causal}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$A$};
\node[main node, left=of 1](4){$\vec{X}$};
 \path[every node/.style={font=\sffamily\small}]
   (4) edge (1)
   (3) edge (2)
   (1) edge (2);
\end{tikzpicture} 
\end{subfigure}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{Y}$ causes $\vec{X}$}
\label{fig:context-graph-anti-causal}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$A$};
\node[main node, left=of 1](4){$\vec{X}$};
 \path[every node/.style={font=\sffamily\small}]
   (1) edge (4)
   (3) edge (2)
   (1) edge (2);
\end{tikzpicture} 
\end{subfigure}
\begin{subfigure}[t]{0.29\textwidth}
\centering
\caption{$\vec{X}$ and $\vec{Y}$ are counfounded}
\label{fig:context-graph-confounded}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
 %nodes
\node[lt](1){$\vec{Y}$};
\node[main node, below=of 1](2){$Y$};
\node[main node, above right=of 2](3){$A$};
\node[main node, left=of 1](4){$\vec{X}$};
\node[lt, below=of 4](5){$U$};
 \path[every node/.style={font=\sffamily\small}]
   (3) edge (2)
   (1) edge (2)
   (5) edge (4) edge (1);
\end{tikzpicture}
\end{subfigure}
\end{figure}

\subsubsection{Learning from logged bandit data}
Another topic of interest within the contextual bandit community, which is deeply connected to causal effect estimation from observational data, is learning from logged bandit feedback data or off-policy evaluation\citep{Langford2008a,strehl2010learning,Li2010,Dudik2011,Bottou2013,Swaminathan2015}. In this setting, the learner has a data set $S = \set{(\vec{X}_t,A_t,\cfb{Y}{A_t})}_{t=1}^T$, which is assumed to have been generated by a stochastic contextual bandit enviroment interacting with some unknown, potentially stochastic, policy $\pi(\vec{x}_t,h_t)$, where $h_t$ is the sequence of observed data up to time $t$. The goal of the learner is to evaluate the value of an alternate policy, $\pi'$, for selecting actions, often with the underlying motivation of identifying an optimal policy within some space of policies $\Pi$.

This problem differs from the contextual bandit problem in that the learner is not interacting with the enviroment. As a result, there is no exploration-exploitation trade-off to be made. However, the problem does not reduce to supervised learning, because the label, $y$ is not the desired . In addition, if $\pi$ is allowed to depend $h$ then the samples are not i.i.d. The majority of the liturature considers the case where the original policy $\pi$ was stationary ($\pi(\vec{x}_t,h_t) = \pi(\vec{x})$). \citet{Langford2008a} do allow the original policy to be adaptive and prove a high probability bound on the accuracy of their estimator for $\pi'$, albeit with the strong assumption that the original estimator $\pi$ did not depend on $\vec{X}$.

If the original policy is assumed to be stationary, the problem of evaluating an alternate policy $\pi'$ is almost identical to that of causal effect estimation under ignorability, discussed in section \ref{sec:causal_effect_under_ignorability}. The causal structure can be represented in figure \ref{fig:off-policy-evaluation} There is an (implicit) assumption that all variables that impact the choice of action by $\pi$ are included in $\vec{X}$, ensuring that $\vec{X}$ statisfies the backdoor criterion with respect to identifying the causal effect of $do(A = a)$ on the observed reward $Y$, for any action $a \in \set{1,...,k}$. The only difference is that the goal is to evaluate alternate policies $\pi'$ that may be stochastic and depend on $\vec{x}$, as opposed to only policies of the form $\pi'(x) = a$, equivelent to $do(A=a)$. However, the identification of such stochastic, conditional policies can be reduced to the identification of $\P{y|do(A=a),\vec{x}}$, see \citet{Pearl2000}, section 4.2. In this case, letting $\Pns{\pi'}{a|\vec{x}}$ denote the distribution over actions under policy $\pi'$ given context $\vec{x}$, the expected (per round) reward obtained by $\pi'$ is given by,

\eqn{
\E{y|\pi'} = \E{y|do(a \sim \pi'(\vec{x}))} = \Esub{(\vec{x},a) \sim \P{\vec{x}}\Pns{\pi'}{a|\vec{x}}}{y|\vec{x},a}
}

As in estimating average causal effects under ignorability, we have a covariate shift problem, with training data sampled from $\P{\vec{x}}\Pns{\pi}{a|\vec{x}}\P{y|\vec{x},a}$ but generalisation error measured with respect to $\P{\vec{x}}\Pns{\pi'}{a|\vec{x}}\P{y|\vec{x},a}$. A difference in practice, is that in the applications frequently considered under learning from logged feedback data, such as ad serving or recommender systems, there may be substantial information available about $\pi$, in the best case, $\Pns{\pi}{a|\vec{x}}$ is known. This makes estimators utilizing inverse propensity weighting, including doubly robust estimators as in \citet{Dudik2011}, more attractive.

\begin{figure}
\centering
\caption{Causal graphical model for learning from logged feedback data under the assumption the original policy $\pi$ for selecting actions was stationary and dependent only on some observed context $\vec{X}$, $a \sim \pi(\vec{x})$}
\label{fig:off-policy-evaluation}
\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1cm,
  thick,main node/.style={observed},lt/.style={latent}]
\node[main node](1){$\vec{X}$};
\node[main node, below right=of 1](2){$Y$};
\node[main node,  below left=of 1](3){$A$};
 \path[every node/.style={font=\sffamily\small}]
   (3) edge (2)
   (1) edge (2) edge (3);
\end{tikzpicture} 
\end{figure}

\citet{Swaminathan2015} point out that the problem of identifying the optimal policy (subject to some risk minimisation goal) is not as simple as estimating the expected reward associated with each policy in some space and selecting the emprical best because the variance of the estimators for some policies may be much higher than for others.
